Poisson approximate likelihood compared to the particle filter

### 2024-08-31 ms.Rnw
minor mod

RUN_LEVEL = 3
NP_MIF       = switch(RUN_LEVEL, 10,   5000,  50000)
NMIF         = switch(RUN_LEVEL, 5,    20,    100)
ncores       = switch(RUN_LEVEL, 4,    10,    36)
top_n_fits   = switch(RUN_LEVEL, 1,    2,     12)
sim_rep      = switch(RUN_LEVEL, 5,    20,    100) #sim_ovov

>>>>

RUN_LEVEL = 2
NP_MIF       = switch(RUN_LEVEL, 10,   5000,  50000)
NMIF         = switch(RUN_LEVEL, 5,    20,    100)
ncores       = switch(RUN_LEVEL, 4,    10,    36)
top_n_fits   = switch(RUN_LEVEL, 1,    2,     12)
sim_rep      = switch(RUN_LEVEL, 5,    20,    100) #sim_ovov
